---
title: "ADNP Script"
author: "Mari Johnson"
date: "06/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(include = TRUE)
knitr::opts_chunk$set(warning = TRUE)

```

# Data Set Up

### Load Packages

```{r load, results='hide', message=F, warning=F}

library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(drc)
library(RColorBrewer)
library(ggforce)
library(reshape2)

```

### Read in data
```{r read data}

setwd("C:/Users/Mari/Documents/R_laptop/2.11.20_TyVac_VAST_repeat")
phago_data <- read.csv("exp_new.csv", fileEncoding="UTF-8-BOM")

```

```{r Str, eval=TRUE}

str(phago_data)

```

### Recode variables

```{r recode}
#factor variables are good for categorising groups, useful for subsequent plotting 
phago_data$Rep <-as.factor(phago_data$Rep)
phago_data$Plate <-as.factor(phago_data$Plate)
phago_data$Visit <- as.factor(phago_data$Visit)

phago_data$Sample_ID <- as.character(phago_data$Sample_ID)
phago_data$Well_ID <- as.character(phago_data$Well_ID)

```

# Data Analysis
### ADNP 

```{r Data analysis}

#divide phago Score by 100
phago_data$Phago_Score <- (phago_data$Phago_Score/100)
      
#compare duplicates, mean, sd and se
      
 phago_data <- phago_data %>% group_by(Sample_ID, Visit, Plate) %>% dplyr::mutate(mean_phago = mean(Phago_Score), sd = sd(Phago_Score), se = sd(Phago_Score) / sqrt(length(Phago_Score)))
      
#Add percent CV column
phago_data<- phago_data %>% group_by(Sample_ID, Visit, Plate) %>% mutate(Percent_CV = sd/mean_phago * 100)
      
      
#Filter for sampes with high %CV
phago_data_CVhigh <- filter(phago_data, Percent_CV > 25)
head(phago_data_CVhigh)

```

### Oxidative Burst
``` {r Oxidative Burst Analysis}

#same as above
phago_data <- phago_data %>% group_by(Sample_ID, Plate, Visit) %>% dplyr::mutate(mean_DHR = mean(DHR), sd = sd(DHR), se = sd(DHR) / sqrt(length(DHR)))
      
#add percent CV column
phago_data<- phago_data %>% group_by(Sample_ID, Visit) %>% mutate(OB_Percent_CV = sd/mean_DHR * 100)
      
      
#data table with high %CV
DHR_CVhigh <- filter(phago_data, OB_Percent_CV > 25)

```

# Data Visualisation

### Standard Curve Check
``` {r Plotting}

#First thing you can check is the serum standard, select serum standard data by it's character name in this case "ss"

phago_data_ss <-filter(phago_data, Sample_ID == 'SS')

phago_data_pp <-filter(phago_data,Sample_ID == 'PP')

#Use package DRC to fit 4PLR curve to data
#input dilutions (if using same dilutions regulary can save as a vector)

ss_curve <-data.frame(Dilution=rep(c(0.025,
                                     0.0125,
                                     0.00625,
                                     0.003125,
                                     0.0015625,
                                     0.00078125)), Phagocytic_Score=c(phago_data_pp$mean_phago))

model1<-drm(Phagocytic_Score~Dilution,
            fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),
            data=ss_curve)
plot(model1)



model1<-drm(Phagocytic_Score~Dilution,
            fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),
            data=ss_curve)
plot(model1)